Analysis paper

### 2021-06-04 analysis/analysis.Rmd
update te code and figures

**Todo** - [ ] maybe remove baseline from relative skill plot - [ ] maybe rearrange plots - [ ] make plots nicer (legend, maybe point size on the left / remove either points or lines)

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Hub-ensemble"
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, scaled_rel_skill, diff_score)][order(target_type, horizon)]

@@

horizons = 2
for (tar in targets) {
  for (i in horizons) {
    name <- paste0(tar, "-", i)

    tmp_df <- df[target_phase == tar & horizon == i, 
                 .(model, interval_score, sharpness,
                   target_phase, horizon, 
                   underprediction, overprediction, 
                   `WIS - median` = interval_score_0.5, 
                   `WIS - sd` = interval_score_sd)]

    tables[[name]] <- make_score_table(tmp_df, 
                                       group = FALSE, 
                                       full_width = FALSE) %>%
      pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)

    save_kable(tables[[name]],
               file = here("analysis", "plots",
                           paste0("table-", gsub(" ", "", name), ".png")))
  }
}

@@

p <- scores_target[model %in% regular_models] %>%
  distribution_plot_wis(x = "bias") + 
  scale_x_continuous() + 
  facet_wrap(~ target_phase, ncol = 3) + 
  geom_vline(xintercept = 0, color = "white", size = 1) + 
  labs(y = "Bias")

>>>>

@@

df <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "horizon", "target_type")
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]

@@

# 
# horizons = 2
# for (tar in targets) {
#   for (i in horizons) {
#     name <- paste0(tar, "-", i)
#     
#     tmp_df <- df[target_phase == tar & horizon == i, 
#                  .(model, interval_score, sharpness,
#                    target_phase, horizon, 
#                    underprediction, overprediction, 
#                    `WIS - median` = interval_score_0.5, 
#                    `WIS - sd` = interval_score_sd)]
#     
#     tables[[name]] <- make_score_table(tmp_df, 
#                                        group = FALSE, 
#                                        full_width = FALSE) %>%
#       pack_rows(tar, 1, nrow(tmp_df), indent = FALSE)
#     
#     save_kable(tables[[name]],
#                file = here("analysis", "plots",
#                            paste0("table-", gsub(" ", "", name), ".png")))
#   }
# }

@@

p <- scores_target[model %in% regular_models] %>%
  distribution_plot_wis(x = "bias") + 
  scale_x_continuous() + 
  facet_wrap(~ target_phase, ncol = 3) + 
  geom_vline(xintercept = 0, color = "black", size = 1.4) + 
  labs(y = "Bias")
